---
title: "WQD7004_GroupProject"
author: "
- HUIJUN LIU (S2142285)

- RUIXUE ZHANG (S2142119)

- KELVIIN RAJJ KARUPAYA (S2151665)

- LINGYU MENG (S2131391)

- ZUOGE CHEN (S2125783)

"
output:
 rmdformats::readthedown:
 self_contained: true
 thumbnails: true
 lightbox: true
 gallery: false
 highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Group No.: 10
## Group Members

* LINGYU MENG (S2131391)

* HUIJUN LIU (S2142285)

* ZUOGE CHEN (S2125783)

* KELVIIN RAJJ KARUPAYA (S2151665)

* RUIXUE ZHANG (S2142119)

## Dataset


* Title: German Credit Risk

* Year: 2020

* Content: This dataset classifies people described by a set of attributes as good or bad credit risks.

* Source: https://www.kaggle.com/datasets/kabure/german-credit-data-with-risk


# 1 Introduction

In this dataset, each entry represents a person who takes a credit by a bank. Each person is classified as good or bad credit risks according to the set of attributes.
 
## 1.1 Project Objective

To manage and avoid the credit risk of users.
  
## 1.2 Project Question

* predict credit amount (regression)

* what variables most related to the credit amount? (classification)

* What level of risk does the customer belong to？

* What is the credit limit of the customer？

# 2 Data Pre-processing

## 2.1 Data Understanding

### Import libraries

```{r import libraries, message=FALSE, warning=FALSE}
library(dplyr)
library(readr)
library(VIM)
library(missForest)
library(Hmisc)
library(caret)
library(ggplot2)
library(e1071)
library(klaR)
library(nnet)
library(Metrics)
library(rpart)
library(tidyverse)
library(skimr)
library(caret)
library(pROC)
library(DataExplorer)
```


### Read data

```{r,message=FALSE}

df = read.csv('file.choose()') 
#Delete the 1st column which is used for indexing.
df=df[,-1]
head(df)

```

### See the structure of dataset

```{r str}
str(df)

```

## 2.2 Handle missing data

### Check missing values

```{r check NAs}
print(paste('Complete obs.:',sum(complete.cases(df))))

```

* Distribution of NAs (by column):

```{r}
colSums(is.na(df))

```

* Check if any missing value is "" type

```{r}
colSums(df=="")

```

### Visualisation of missing part

```{r VIM}
aggr(df,labels=names(df),col=c('blue','red'),
     numbrs=T,sortVars=T)

```

As shown above, Saving.accounts & Check.account contain missing values, and red color presents missing part.

### Predict and impute NAs

**Step 1: Convert chr variables to factor type**

```{r convert type}
df1 <- df
df1$Sex <- as.factor(df1$Sex)
df1$Job <- as.ordered(df1$Job)
df1$Housing <- as.factor(df1$Housing)
df1$Saving.accounts <- as.ordered(df1$Saving.accounts)
df1$Checking.account <- as.ordered(df1$Checking.account)
df1$Purpose <- as.factor(df1$Purpose)
df1$Risk <- as.ordered(df1$Risk)

```


**Step 2: Impute NAs using missForest**

**missForest** is used to impute missing values particularly in the case of mixed-type data. It can be used to impute **continuous and/or categorical** data including complex interactions and nonlinear relations. It yields an out-of-bag (OOB) imputation error estimate. Moreover, it can be run parallel to save computation time.  
  
```{r missForest}
df.mis <- df1[!complete.cases(df1),]
df.train <- df1[complete.cases(df1),]
set.seed(42)
df.imp <- missForest(xmis = df.mis, xtrue = df.train, maxiter = 10, ntree = 200)
message('Out of Bag error: ', df.imp$OOBerror)

```

**Save imputation result**

```{r impute}
df.nomis <- df1
df.nomis[!complete.cases(df.nomis),] <- df.imp$ximp

```

**Saving.Account values distribution after imputation:**

```{r}
table(df.nomis$Saving.accounts)

```

**Checking.Account values distribution after imputation:**

```{r}
table(df.nomis$Checking.account)

```

## 2.3 Smooth noisy data (Not yet decided)

```{r eval=FALSE, include=FALSE}
Age_bp <- boxplot(df.nomis$Age,boxwex=0.7)
Age_bp$out
CredAmt_bp <- boxplot(df.nomis$Credit.amount, boxwex=0.7)
CredAmt_bp$out
Duration_bp <- boxplot(df.nomis$Duration,boxwex=0.7)
Duration_bp$out
```


* Save cleaned dataset

```{r save dataset}
write.csv(df.nomis,file = 'german_credit_data_rmna.csv',row.names=F)

```

* Summary dataset

```{r summary}
summary(df.nomis)

```



### Descriptions of cleaned dataset

* Age: (quantitative, in years)
* Sex: (dichotomous: female, male)
* Job: (ordinal: 0 - unskilled and non-resident, 1 - unskilled and resident, 2 - skilled, 3 - highly skilled)
* Housing: (nominal: own, rent, or free)
* Saving.accounts: (ordinal: little, moderate, quite rich, rich) - Status of existing saving account.
* Checking.account: (ordinal: little, moderate, rich) - Status of existing checking account.
* Credit.amount: (quantitative, in D-mark) The maximum amount that the bank is committed to lend.
* Duration: (quantitative, in month) The specified time to pay the credit.
* Purpose: (nominal: car, furniture/equipment, radio/TV, domestic appliances, repairs, education, business, vacation/others) - Reasons to get a loan.
* Risk: (dichotomous : good, bad)


# 3 Exploratory Data Analysis

## 3.1  show the relationship between the duration of credit and the credit amount

```{r}
Dur_Cred_Plot<-ggplot(df.nomis, aes(x=Duration, y=Credit.amount))+geom_point()
Dur_Cred_Plot

```

## 3.2 show the relationship between the sex and the credit amount

```{r}
Sex_Cred_Plot<-ggplot(df.nomis,aes(x=Sex, y=Credit.amount))+geom_jitter(size=2, alpha=0.5)
Sex_Cred_Plot

```

## 3.3 analyse the relationship between duration of credit and age

```{r}
Dur_Age_Plot<-ggplot(df.nomis,aes(x=Duration, y=Age, color=Risk))+geom_point()+geom_smooth()
Dur_Age_Plot

```

## 3.4 display points in scatter plot for bad and good loans

```{r}
Dur_Cred_Risk_Plot<-ggplot(df.nomis,aes(x=Duration,y=Credit.amount))+geom_point(aes(color=Risk))
Dur_Cred_Risk_Plot

```

## 3.5 use faceting to split entire graph into 2 separate panels for each, good and bads loans

```{r}
Dur_Cred_Risk_facetPlot<-ggplot(df.nomis,aes(x=Duration, y=Credit.amount))+geom_point()+geom_smooth(se=F)+
  facet_grid(.~Risk)
Dur_Cred_Risk_facetPlot

```

## 3.6 check how the Job variable impacts the credit

```{r}
Dur_Cred_Risk_Job_Plot<-ggplot(df.nomis,aes(x=Duration, y=Credit.amount, color=Job))+geom_point()+geom_smooth(se=F, method="lm")+
  facet_grid(.~Risk)
Dur_Cred_Risk_Job_Plot

```

## 3.7 facet to split the graph into the 4 type job variables

```{r}
Dur_Cred_Risk_Job_facetPlot<-ggplot(df.nomis,aes(x=Duration, y=Credit.amount, color=Risk))+geom_point()+geom_smooth(se=F, method="lm")+
  facet_grid(.~Job)
Dur_Cred_Risk_Job_facetPlot

```

## 3.8 show relationship between the savings account and credit amount

```{r}
Sav_Cred_Plot<-ggplot(df.nomis,aes(x=Saving.accounts, y=Credit.amount))+geom_bar(stat="identity")
Sav_Cred_Plot

```

## 3.9 show the good and bad loans in each savings account category

```{r}
Sav_Cred_Risk_Plot<-ggplot(df.nomis,aes(x=Saving.accounts, y=Credit.amount, fill=Risk))+geom_bar(stat="identity", position=position_dodge())
Sav_Cred_Risk_Plot

```
## 3.10 analyse the good and bad loans in the relationship between duration of credit and credit amount using the housing variable

```{r}
Dur_Cred_House_Risk<-ggplot(df.nomis,aes(x=Duration, y=Credit.amount))+geom_point()+geom_smooth()+
  facet_grid(Housing~Risk)
```


```{r}
Dur_Cred_House_Risk
```


# 4 Modeling
## 4.1 Regression Model  predict credit amount (regression)
```{r}
df2 = read.csv(file.choose()) 

```

```{r}
skim(df.nomis)
```
```{r}
# Check the missing data
plot_missing(df.nomis)
```
```{r}
class(df2)
```
```{r}
head(df.nomis)
```


```{r}
# feature engineering
# Train/Test split for Regression
train1 <-createDataPartition(y=df.nomis$Credit.amount,p=0.7,list=FALSE)

train <- df2[train1, ]

test <- df2[-train1, ]

# fold cross validation
train_control <- trainControl(method="cv", number=10)
```
### simple linear regression model
```{r}
fit <- lm(Credit.amount ~ Age,data = df.nomis)
summary(fit)
```

```{r}
plot(df.nomis$Age,df.nomis$Credit.amount)
abline(fit) 
```

### multiple linear regression model
```{r}
fit2 <- lm(Credit.amount ~ Age+Sex+Job+Housing+Saving.accounts+Checking.account,data = df.nomis)
summary(fit2)
```
```{r}
anova(fit,fit2)
```
```{r}
# ridge regression
set.seed(42)
model_ridge <- train(Credit.amount~ Age+Sex+Job+Housing+Saving.accounts+Checking.account,data= train, trControl=train_control,method="ridge", metric="RMSE")
model_ridge
```
```{r}
set.seed(42)
model_lars <- train(Credit.amount~ Age+Sex+Job+Housing+Saving.accounts+Checking.account,data= train, trControl=train_control,method="lars", metric="RMSE")
model_lars
```
Evidently, least angle regression has the smaller RMSE and we will choose it as our prediction model. Similarly, we will confirm whether our model is overfitting.
```{r}
# Make predictions on the testing dataset
x_test_reg <- df.nomis[,1:6 ]
y_test_reg <- df.nomis[, 7]
prediction_lars <- predict(model_lars,x_test_reg)
RMSE(prediction_lars, y_test_reg)
```
Conclusion:
We could see both RMSE are about 2570.894 and perform almost the same with the model trained on all features. Thus we could predict the Credit.amount with this model especially considering a vast amount of data.



